Shaping the Perception of a Robot by Cognitive Priming

### 2016-05-17 rebuttal.tex

\documentclass{article}
\usepackage[utf8]{inputenc}

\begin{document}

Dear Editor, Dear Reviewers,

\vspace{2em}

We would like first to thank the editor and the reviewers for their thorough review of our
work. The manuscript underwent significant changes: we have hopefully addressed most of
the reviewers' concerns, and we discuss hereafter the remaining points.

The core points raised by the editors were the following:

\begin{itemize}
    \item \emph{Lack of theoretical background for the concept of "cognitive
        context"}: we take this point, and have reframed our theoretical
        background around "cognitive priming". Section 1.1 accordingly provides
        the literature references and precisely define our shallow vs deep
        conditions.
    \item \emph{Validity of the manipulation check} TBD
    \item \emph{Missing material}: We have appended the pre- and
        post-questionnaires to the manuscript appendices. We have as well added
        a link to the video stimuli, and eye-tracking and questionnaires
        results.
    \item \emph{Cursory eye-tracking results}: we have significantly expanded
        our reporting of eye-tracking results [TBD add details]
    \item \emph{Curiosity about cognitive skills vs actual ascription of cognitive
        skills}: one question raised concerns whether the participants are
        actually ascribing cognitive capacities to the robot, or merely curious
        whether the robot has them or not. While our approach does not
        intrinsically allow to rule out one or the other of these
        interpretations, we argue that this issue is to be observed in virtually
        any short-term human-robot interaction: as we previously
        argued~\cite{lemaignan2014cognitive}, the initial human-robot cognitive
        familiarisation period is basically about restating and iteratively
        shaping a mental model of the robot. During that period of time,
        anthropomorphic \emph{projections} are likely not yet anthropomorphic
        \emph{ascriptions}, and any investigation of anthropomorphism at this
        stage is subject to this double interpretation ``curiosity'' vs
        ``ascription''. In order to rule out one of the interpretation,
        longer-term observations (once the novelty effect has vanished) are
        needed, which could be relatively easily conducted with our method (by
        relying on non-intrusive gaze tracking techniques). [TBD: Kshitij
        argument]
    \item \emph{Use of the concept of proxy}: Using the term ``proxy'' was a
        mistake, rightfully pointed by the editor. This has been removed from
        the text.

\end{itemize}

The introduction of the article has been largely rewritten, to better frame our
work, and to clarify our working hypotheses.

We have as well attempted to address individually each of the other concerns
raised by the reviewers in this document (note that minor typos/style issues
have been fixed directly in the manuscript, and are not discussed here).

\section{Comments from Editor}

We list hereafter the main points raised by the editor (the other ones, omitted
here for brevity, have been directly addressed in the text):

\begin{itemize}
    \item \emph{Computation of the gazing differences between the human and the
        robot conditions}: TBD
    \item \emph{Choice of the questionnaire result subset}: TBD
    \item \emph{Possible ordering effect in the manipulation check}: TBD
    \item \emph{Interpretation of the head fixation in the 'deep cognitive
        priming' condition}: the editor suggests that the interpretation of the
        head focus in terms of higher anthropomorphic ascriptions onto the robot
        depends on the meaningfulness of such a head focus for a human. As noted
        in the paper, we did not observed significant differences in fixations
        on the human head between the shallow and deep cognitive conditions. We
        interpret this absence of difference as the result of the mere presence
        of a human being: because of the human presence, the two conditions
        (deep vs shallow) do not elicit anymore a significantly different perception of
        the situation as being machine-like or human-like. As such
        such a strong intrinsic source of

\end{itemize}

All the other grammar and style errors pointed by the editor have been addressed.

\bibliographystyle{abbrv}
\bibliography{biblio}

\end{document}

### 2016-05-18 main.tex
Cognitive priming
Added some studies about priming and rationale for the deep and shallow
priming.

\textbf{TBD: Kshitij} at the end of this section, the reader must be convinced
that:
\begin{itemize}
    \item cognitive priming is a well established technique, grounded in the
        literature,
    \item our terminology ('shallow' vs 'deep') is meaningful, and grounded
    \item our cognitive priming would impact the perception of the interaction
        situation as machine-like vs human-like (to support our manipulation
        check!)
\end{itemize}

@@

Running an ANOVA against the change of anthropomorphic attributions
(\deltaant) over the duration of the experiment in the two cognitive
conditions, shows that \deltaant is greater for tasks with a deeper cognitive
context than that for the shallow cognitive tasks ($F(1,54) = 6.54, p <
.05$\fixme{put the exact p value here},
figure~\ref{h4}). In other words, after being exposed to short videos of a robot
performing simple tasks, participants primed with a deeper cognitive
expectations report a significantly higher tendency to anthropomorphise robots
\emph{in general} (as the questionnaire on anthropomorphic attributions
explicitly referred to \emph{robots in general}).

\begin{figure}
    \centering
    \includegraphics[width=3.3in]{H4}\label{ICAtoAAPImprovement}
    \caption{Difference between \anti{} and \antf{} in the shallow and deep
    cognitive priming conditions.}
    \label{h4}
\end{figure}

This result supports \h{4} and validate that the cognitive priming impacts the
attribution of anthropomorphic features to robots. This, in turn, supports the
\emph{proxy} hypothesis of \h{3}: \emph{head fixations are a proxy for higher
levels of human-likeness attributions}.

>>>>

Previous studies had shown that cognitive and/or affective priming influences human perception of the input stimulus. \cite{zajonc1980feeling} advocated the the use of affective priming and proposed that the affective reactions can be elicited with minimal stimulated input. As \cite{murphy1993affect} wrote \textit{``The experimental paradigm of priming, involves the presentation of one stimulus, or prime, alters subjects' perceptions of a second target stimulus...''}  \cite{murphy1993affect} found in their series of studies, where the subjects were shown happy and angry faces of people as a priming method, showed that the subjects' perceptions of positive emotions were higher and quicker when the priming was a happy face than for those who were primed with a angry face. The gender of the priming faces, however had no effect on the subjects' perception.

\cite{forgas1987mood} showed that priming subjects with positive or negative moods affects their person-perception judgement\footnote{Person-perception judgement is a task where the subjects are asked to read a few characteristics of an unknown person; and once they have read the description the subjects are then asked to provide their perception about the target person}. In their study, \cite{forgas1987mood} showed used a bogus test with manipulated positive or negative feedback to prime the mood of the subjects in a positive or negative manner. Once the subjects were primed with a particular mood they were shown the descriptions of some unknown persons (with the same positive and negative characteristics). The results showed that the mood priming influences their person-perception, i.e, the positively primed subjects gave more positive remarks about the target perception while the negatively primed subjects gave more negative remarks. Moreover, the subjects in both the priming conditions spent more time on the priming specific characteristics (positive or negative). This shows that not only subjects' perception was altered but also their approach as well using the mood priming.

\cite{yi1990cognitive} used specific attributes of a car to prime subjects' before they watched an advertisement about cars. The advertisement focused on explains various characteristics of a few imaginary cars in terms of the safety and the fuel efficiency. The priming stimulus had the size of the cars manipulated. The results showed that tone (affective priming) and size (cognitive priming) affects the favourability of the cars. For example, a big car was perceived to be more ``safe'' and less ``fuel-efficient'' than the small cars.

\cite{tillmann2006cognitive}, in an fMRI study with music notes, showed that different parts of the frontal cortex gets activated when the participants were primed with sung or instrumental music. In their experiment, the subjects were asked to listen the first seven notes in either sung or instrumental manner (cognitive priming) and then to identify the relation between the first seven and the eighth note. The results showed that the subjects showed a higher activation in the inferior frontal cortex when primed with the sung notes than when they were primed with the instrumental notes. \cite{rholes1987emotional} showed that the memory recall is affected by the tone (affective priming) of the self-evaluation statement. In an experiment, where the subjects were given a set of positive or negative self-evaluation statements before being asked to recall a few good and bad memories from their past, the subjects were faster in recalling good memories when they were given a positive self-evaluation test; and vice-versa.

All the above studies show that the cognitive and/or affective priming might alter the behaviour and/or the perception of the subjects about a target stimulus. Some of the studies found some complex interactions between cognitive and affective priming (\cite{yi1990cognitive} and \cite{storbeck2008affective} ). In this contribution, we were only interested in the cognitive priming aspect during a Human Robot Interaction situation, as \cite{baldwin1990priming} advocated that the cognitive priming may activate a relationship schema between the priming stimulus and the target stimulus. Moreover, in the context of advertisement, a number of studies suggest that the ad context (cognitive priming) can influence the audience's perception of the ad, and thus, its effectiveness (e.g., \cite{singh1987arousal};\cite{soldow1981response})  Our primary hypothesis was that the way the robot is given commands might alter the way the subjects perceive its actions. We propose to use a neutral mood (no affective priming) and two cognitive priming conditions (Deep and Shallow), in order to remove the ``mood'' or  ``affect'' bias of the priming. The ``shallow'' priming consisted of giving commands to the robot which are more ``machine-like''. On the other hand, the ``deep'' priming had the commands to robot in a more ``human-like'' manner (Manipulation-check hypothesis). We also kept the time of priming to be the same in the deep and shallow conditions, in order to remove the time of priming effect on the subjects' perceptions about the robot.

@@

Running an ANOVA against the change of anthropomorphic attributions
(\deltaant) over the duration of the experiment in the two cognitive
conditions, shows that \deltaant is greater for tasks with a deeper cognitive
context than that for the shallow cognitive tasks ($\Delta_{shallow}=TBD (SD=TBD)$
\vs $\Delta_{deep}=TBD (SD=TDB)$, $F(1,54) = 6.54, p < .05$\fixme{put the exact
p value here}). In other words, after being exposed to short videos of a robot
performing simple tasks, participants primed with a deeper cognitive
expectations report a significantly higher tendency to anthropomorphise robots
\emph{in general} (as the questionnaire on anthropomorphic attributions
explicitly referred to \emph{robots in general}).

%\begin{figure}
%    \centering
%    \includegraphics[width=3.3in]{H4}\label{ICAtoAAPImprovement}
%    \caption{Difference between \anti{} and \antf{} in the shallow and deep
%    cognitive priming conditions.}
%    \label{h4}
%\end{figure}

This result supports \h{4}: cognitive priming impacts the
attribution of anthropomorphic features to robots \emph{beyond the specific Nao robot
shown in the stimuli}.  It appears that participants transfer to some extent the
cognitive capabilities that they ascribe to the Nao robot in the
\emph{deep} cognitive condition to ``robots'' in general (we can not, however,
conclude on any possible \emph{lasting} anthropomorphic ascriptions to robots as we
measure the anthropomorphic perception immediately after the experiment).
